working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-09 Manuscript_draft/Manuscript_draft.Rmd
Getting rid of outliers
edits

@@

Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values). Heterospecific pollen reduced seet set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Moreover, effect sizes differ across species, see **Figure 2** where species like *S. lycopersicum* had a large effect size and other's like *E. sativa* a small or null effect size.

Across families we found a very similar effect but when species where look at species level they respond differently even within the same family [rephrase and maybe test statistically?](), for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine. The 100% foreign pollen treatments barely produced seeds or fruits [and just for *Sinapis alba* we did not find significant differences between the hand cross-pollination and one treatment with pollen from a confamilial- IB Unclear](). Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases [under which treatment](). *S. lycopersicum* seems to produced small fruits (35% of the treatments) independently of pollen and pollen donor due to also apomictic treatments did, never normal size. *C. annuum* produced some fruits (9%) of both small and normal size and finally *S. melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with treatments that tested for apomixis.[clarify this descriptive statistics part- Also a figure with a summary of the treatments effect would be cool, or at least in the appendices]()

@@

#CAAN
load("effect_size_species/caan_effect_size.RData")
p7<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,0.5,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "G)")

#PEIN
load("effect_size_species/pein_effect_size.RData")
p8<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,1,0.5,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "H)")

>>>>

Mention that SI index is calculated (Schoen & Lloyd 1984)

@@

Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values). Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Moreover, average effect sizes differed across species and families, see **Figure 2**. Despite some variability in the effect of the different pollen donors per species, in general terms the effect per species was homogeneous (see **Figure 3**). When the donors were groped by family not big differences were seen, just for one species

 The 100% foreign pollen treatments barely produced seeds or fruits [and just for *Sinapis alba* we did not find significant differences between the hand cross-pollination and one treatment with pollen from a confamilial- IB Unclear](). Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases [under which treatment](). *S. lycopersicum* seems to produced small fruits (35% of the treatments) independently of pollen and pollen donor due to also apomictic treatments did, never normal size. *C. annuum* produced some fruits (9%) of both small and normal size and finally *S. melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with treatments that tested for apomixis.[clarify this descriptive statistics part- Also a figure with a summary of the treatments effect would be cool, or at least in the appendices]()

@@

#CAAN
load("effect_size_species/caan_effect_size.RData")
p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,0.5,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "G)")

#PEIN
load("effect_size_species/pein_effect_size.RData")
p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,1,0.5,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "H)")

### 2019-03-09 Manuscript_draft/Manuscript_draft.tex
edits

@@

Results of hand cross-pollination, hand self-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seet set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05. Moreover, effect
sizes differ across species, see \textbf{Figure 2} where species like
\emph{S. lycopersicum} had a large effect size and other's like \emph{E.
sativa} a small or null effect size.

Across families we found a very similar effect but when species where
look at species level they respond differently even within the same
family \href{}{rephrase and maybe test statistically?}, for instance for
two species of the Brassicaceae family \emph{Brassica oleracea} and
\emph{Eruca versicaria} we found very contrasting effects of foreign
pollen where for the first one, all donors reduce seed set
significatively and for the second, just two species did out of nine.
The 100\% foreign pollen treatments barely produced seeds or fruits
\href{}{and just for \emph{Sinapis alba} we did not find significant
differences between the hand cross-pollination and one treatment with
pollen from a confamilial- IB Unclear}. Solanaceae species with berry
fruit type developed small fruits or even normal fruits in some cases
\href{}{under which treatment}. \emph{S. lycopersicum} seems to produced
small fruits (35\% of the treatments) independently of pollen and pollen
donor due to also apomictic treatments did, never normal size. \emph{C.
annuum} produced some fruits (9\%) of both small and normal size and
finally \emph{S. melongena} produced seedless normal fruits with just
confamilial pollen (3\%), for both species seems that fruit formation
was induced by pollen on the stigma because of lack of fruit production
with treatments that tested for apomixis.\href{}{clarify this
descriptive statistics part- Also a figure with a summary of the
treatments effect would be cool, or at least in the appendices}

>>>>

Mention that SI index is calculated (Schoen \& Lloyd 1984)

@@

Results of hand cross-pollination, hand self-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seed set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05. Moreover, average
effect sizes differed across species and families, see \textbf{Figure
2}. Despite some variability in the effect of the different pollen
donors per species, in general terms the effect per species was
homogeneous (see \textbf{Figure 3}). When the donors were gropued by
family not big differences were seen, just for one species

The 100\% foreign pollen treatments barely produced seeds or fruits
\href{}{and just for \emph{Sinapis alba} we did not find significant
differences between the hand cross-pollination and one treatment with
pollen from a confamilial- IB Unclear}. Solanaceae species with berry
fruit type developed small fruits or even normal fruits in some cases
\href{}{under which treatment}. \emph{S. lycopersicum} seems to produced
small fruits (35\% of the treatments) independently of pollen and pollen
donor due to also apomictic treatments did, never normal size. \emph{C.
annuum} produced some fruits (9\%) of both small and normal size and
finally \emph{S. melongena} produced seedless normal fruits with just
confamilial pollen (3\%), for both species seems that fruit formation
was induced by pollen on the stigma because of lack of fruit production
with treatments that tested for apomixis.\href{}{clarify this
descriptive statistics part- Also a figure with a summary of the
treatments effect would be cool, or at least in the appendices}
